---
title: "QnD Analysis - Gait Annotation - Gait Features"
output:
  pdf_document: default
  html_notebook: default
---

This notebook will cover some of the QnD analysis of the gait annotations and how it acts towards the PDKit Gait Feature package.

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("EDA.R")
```

# Concordance Matrix
```{r warning=FALSE,echo=FALSE}
walk <- annot_data %>%
    yardstick::conf_mat("walk_status.x", "walk_status.y") %>% 
    tune::autoplot(type = "heatmap") + 
    labs(title = "Walk Concordance",
         x = "annotator 1",
         y = "annotator 2") +
    theme_minimal() + 
    theme(plot.title = element_text(size = 16, face = "bold"),
          axis.title.x = element_text(size = 12, face = "bold"),
          axis.title.y = element_text(size = 12, face = "bold"))
pocket <- annot_data %>%
    yardstick::conf_mat("pocket_status.x", "pocket_status.y")  %>% 
    tune::autoplot(type = "heatmap") + 
    labs(title = "Pocket Concordance",
         x = "annotator 1",
         y = "annotator 2") +
    theme_minimal() + 
    theme(plot.title = element_text(size = 16, face = "bold"),
          axis.title.x = element_text(size = 12, face = "bold"),
          axis.title.y = element_text(size = 12, face = "bold"))

wrap_plots(walk, pocket, nrow = 2)
```

# Breaking Down Diagnosis Status of each group
```{r}
annot_with_demo %>% 
    dplyr::group_by(walk_group_status, diagnosis) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::ungroup() %>%
    tidyr::pivot_wider(names_from = diagnosis, values_from = n) %>% 
    dplyr::inner_join(get_permutations_group(walk_factor), 
                      by = c("walk_group_status"="group_status")) %>%
    knitr::kable("pipe")

annot_with_demo %>% 
    dplyr::group_by(pocket_group_status, diagnosis) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::ungroup() %>%
    tidyr::pivot_wider(names_from = diagnosis, values_from = n) %>% 
    dplyr::inner_join(get_permutations_group(pocket_factor), 
                      by = c("pocket_group_status"="group_status")) %>%
    knitr::kable("pipe")

```


# Proportion of NA of both Agreements:
Calculated by grouping each recordId and for each recordId, summarize each dataframe by proportion of NA (Total NA/(nrow * ncol))
```{r}
NA_prop_plot
```

# Feature Distribution: Cadence
Calculated by taking the cadences and box plot the two groups. No aggregations here. 
```{r}
plots_walk_status$cadence
plots_pocket_status$cadence
```

# Feature Distribution: Step/Stride Durations
```{r}
plots_walk_status$step_duration
plots_pocket_status$step_duration
plots_walk_status$stride_duration
plots_pocket_status$stride_duration
```

# Comparing Adherences
This plot compares 3 different classes:
    - Adherence: Agreed in-pocket, agreed walking
    - Non Adherence: Negation(Adherence)
    - In Between: Everything Else
```{r}
plots_combined_status$cadence
```


