# Feature Extraction - Tapping

This wiki page is used to describe the data extracted for the tapping features information/description/QC processes. It will cover the following:

* Wiki Info
* Tapping Feature Description
* QC for each extracted feature files (queried from provenance documentation)

```{r, include = FALSE}
library(synapser)
library(tidyverse)
library(knit2synapse)

synapser::synLogin()
```

```{r, include = FALSE}
FOLDER_ID  <- "syn26215075"
```

### Wiki Info
```{r, message = FALSE, echo=FALSE}
user = synapser::synGetUserProfile()$userName
createdOn = lubridate::now() %>% strftime()

data <- tibble::tibble(
    metadata = c("generated_by", "createdOn"),
    value = c(user, createdOn)
)

knitr::kable(data, "pipe")
```


### Feature Description:

| Feature Name      | Definition                                                                                        |
| ----------------- | ------------------------------------------------------------------------------------------------- |
| meanTapInter      | mean tapping interval                                                                             |
| medianTapInter    | median tapping interval                                                                           |
| iqrTapInter       | interquartile range tapping interval                                                              |
| minTapInter       | minimum tapping interval                                                                          |
| maxTapInter       | maximum tapping interval                                                                          |
| skewTapInter      | skewness tapping interval                                                                         |
| kurTapInter       | kurtosis tapping interval                                                                         |
| sdTapInter        | standard deviation tapping interval                                                               |
| madTapInter       | mean absolute deviation tapping interval                                                          |
| cvTapInter        | coefficient of variation tapping interval                                                         |
| rangeTapInter     | range tapping interval                                                                            |
| tkeoTapInter      | teager-kaiser energy operator tapping interval                                                    |
| ar1TapInter       | autocorrelation (lag = 1) tapping interval                                                        |
| ar2TapInter       | autocorrelation (lag = 2) tapping interval                                                        |
| fatigue10TapInter | difference in mean tapping interval between the first and last 10% of the tapping interval series |
| fatigue25TapInter | difference in mean tapping interval between the first and last 25% of the tapping interval series |
| fatigue50TapInter | difference in mean tapping interval between the first and last 50% of the tapping interval series |
| meanDriftLeft     | mean drift in the left button                                                                     |
| medianDriftLeft   | median drift in the left button                                                                   |
| iqrDriftLeft      | interquartile range of drift in the left button                                                   |
| minDriftLeft      | minimum of drift in the left button                                                               |
| maxDriftLeft      | maximum of drift in the left button                                                               |
| skewDriftLeft     | skewness of drift in the left button                                                              |
| kurDriftLeft      | kurtosis of drift in the left button                                                              |
| sdDriftLeft       | standard deviation of drift in the left button |
| madDriftLeft      | mean absolute deviation of drift in the left button |
| cvDriftLeft       | coefficient of variation of drift in the left button |
| rangeDriftLeft    | range of drift in the left button |
| meanDriftRight    | mean drift in the right button |
| medianDriftRight  | median drift in the right button |
| iqrDriftRight     | interquartile range of drift in the right button |
| minDriftRight     | minimum of drift in the right button |
| maxDriftRight     | maximum of drift in the right button |
| skewDriftRight    | skewness of drift in the right button |
| kurDriftRight     | kurtosis of drift in the right button |
| sdDriftRight      | standard deviation of drift in the right button |
| madDriftRight     | mean absolute deviation of drift in the right button |
| cvDriftRight      | coefficient of variation of drift in the right button |
| rangeDriftRight   | range of drift in the right button |
| numberTap         | number of taps |
| buttonNoneFreq    | frequency where neither the left or right buttons were hit |
| corXY             | correlation between the X and Y coordinates of the hits |


### Feature QC Documentation:
```{r, echo=FALSE}
data <- synGetChildren(FOLDER_ID)$asList() %>%
    purrr::map_dfr(function(x){
        id <- x$id
        name <- x$name
        provenance <- synGetProvenance(id)
        description <- provenance$get("description")
        tibble::tibble("id" = id,
                       "file_name" = name,
                       "description" = description)
    })

knitr::kable(data, "pipe")
```

