# Feature Extraction - Tapping

This wiki page is used to describe the data extracted for the tapping features information/description/QC processes. It will cover the following:

* Wiki Info
* Tapping Feature Description
* Feature Aggregation
* Documentation

```{r, include = FALSE}
library(synapser)
library(tidyverse)
library(knit2synapse)

synapser::synLogin()
```

```{r, include = FALSE}
FOLDER_ID  <- "syn26262362"
```

### Wiki Info
```{r, message = FALSE, echo=FALSE}
user = synapser::synGetUserProfile()$userName
createdOn = lubridate::now() %>% strftime()

data <- tibble::tibble(
    metadata = c("generated_by", "createdOn"),
    value = c(user, createdOn)
)

knitr::kable(data, "pipe")
```


### Feature Description:
Refer to https://www.synapse.org/#!Synapse:syn26215075

### Aggregation:

* {features}_iqr: summarized by interquartile of contributed tapping activities
* {features}_md: summarized by median of contributed tapping activities

### Documentation:
```{r, echo=FALSE}
data <- synGetChildren(FOLDER_ID)$asList() %>%
    purrr::map_dfr(function(x){
        id <- x$id
        name <- x$name
        provenance <- synGetProvenance(id)
        description <- provenance$get("description")
        tibble::tibble("id" = id,
                       "file_name" = name,
                       "description" = description)
    })

knitr::kable(data, "pipe")
```