
## UDALL Super Users Feature Dictionary
Maintainer: aryton.tediarjo@sagebase.org

```{r, include = FALSE}
library(knit2synapse)
library(synapser)

synapser::synLogin()
```

```{r, include= FALSE}
walk_data <- tibble::tibble(
    "features" = c("AA_speed_of_gait_{aggregation}",
                   "{axis}_cadence_{aggregation}",
                   "{axis}_step_duration_{aggregation}",
                   "{axis}_stride_duration_{aggregation}",
                   "{axis}_step_deviation_{aggregation}",
                   "{axis}_stride_deviation_{aggregation}",
                   "rotation_omega"
    ),
    "description" = c(
        "It extracts the gait speed from the energies of the approximation coefficients of         wavelet functions. Uses the magnitude of x, y and z (mag_acc_sum) here, as the            time series.",
        "The number of steps per window duration",
        "Duration between detected steps-to-step in seconds",
        "Duration between detected stride-to-stride pattern in seconds",
        "Standard Deviation between step-to-step pattern",
        "Standard Deviation between stride-to-stride pattern",
        "Rotation Speed"
    )
)


tap_data <- tibble::tibble(
    "features" = c('meanTapInter', 
                'medianTapInter', 
                'iqrTapInter',
                'numberTaps',
                'tkeoTapInter',
                'fatigue50TapInter',
                'fatigue25TapInter',
                'fatigue10TapInter'),
    "description" = c(
        "mean tapping interval",
        "median tapping interval",
        "interquartile range tapping interval",
        "number of taps",
        "teager-kaiser energy operator tapping interval",
        "difference in mean tapping interval between the first and last 50% of the tapping interval series",
        "difference in mean tapping interval between the first and last 25% of the tapping interval series",
        "difference in mean tapping interval between the first and last 10% of the tapping interval series"
    )
)

tremor_data <- tibble::tibble(
    "features" = c("cent.fr.iqr_ud_accelerometer",
                   "Q75.fr.iqr_uj_accelerometer",
                   "mean.tm.iqr_uavacf_gyroscope"),
    "description" = c(
        "Centroid of the frequency spectrum of user displacement from accelerometer reading, summarized using IQR across moving window in the time series",
        "75th Quartile of the frequency spectrum of user jerk from accelerometer reading, summarized using IQR across moving window in the time series",
        "Mean gyroscope reading, where it is assessed based on autocorrelation of the time-series and summarized using IQR across moving window in the time series"
    )
)


metadata <- tibble::tibble(
    column = c("externalId", "diagnosis", "age", "recordId", "activityType", "medTimepoint"),
    description = c("External ID/User ID used across projects",
                    "Diagnosis of PD/Controls",
                    "Age of user",
                    "The user unique contributed activities",
                    "The column declaring what activity is being recorded",
                    "Medication Timepoint of when activity is being recorded")
    
)

pd_scores <- tibble::tibble(
    column = c("PD_severity_score"),
    description = c(paste(
        "PD severity scores assessed from model prediction probabilities,",
        "model is trained based on our cohort's walk30seconds and tapping activities.",
        "0: low PD severity score - 100: high PD severity score"
        )
    )
)
```

# Metadata
```{r, echo = FALSE}
knitr::kable(metadata, "pipe")
```


# PD Severity Score
```{r, echo = FALSE}
knitr::kable(pd_scores, "pipe")
```



# Walk 30 seconds

Notation for walk 30 seconds features:
- {axis}: the direction of the sensor recording: x,y,z, AA (magnitude)
- {aggregation}: aggregate scores (median, interquartile) of moving windows for each participant recordIds. *Note: Moving window is used to featurize walk activity for every 5 seconds  

```{r, echo = FALSE}
knitr::kable(walk_data, "pipe")
```

# Tapping Activity
```{r, echo = FALSE}
knitr::kable(tap_data, "pipe")
```

# Tremor Activity
```{r, echo = FALSE}
knitr::kable(tremor_data, "pipe")
```


